Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

\begin{lemma} \label{lmm:hv:type1:properties}
    %Let $r_i$ be the full rectangle of $r_i'$ for each $i \in [k-2]$.
    All the following statements are true:
    \myenums{
        \item For each $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$, we have:

        \myenums{
            \item $\dcross_H(\bm{t}) \ne \emptyset$ and $\dcross_V(\bm{t}) \ne \emptyset$.

            \item Denote by $r_i$ ($i \in [k-2]$) the full rectangle of $\bm{t}[i]$. 
            For any $h \in \dcross_H(\bm{t})$ and any $v \in \dcross_V(\bm{t})$, the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.
        }

        \item Consider any a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v) \in \J_1$. Let $r'_i$ ($i \in [k-2])$ be the trimmed rectangle of $r_i$, and set $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2})$. Then, $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$, $h \in \dcross_H(\bm{t})$, and $v \in \dcross_V(\bm{t})$.

@@

By statements (b) and (2) of Lemma~\ref{lmm:hv:type1:properties}, the set $\J^*$ thus computed indeed satisfies \eqref{eqn:hv:type1:J*}. Furthermore, if we are given $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ for each $\bm{t}$, statement (a) of Lemma~\ref{lmm:hv:type1:properties} assures us that the above algorithm runs in $O(1 + k \cdot |\J^*|) = O(1 + k \cdot \out)$ time.

@@

\extraspacing {\bf Computing the ``d-cross'' Sets.} We are ready to compute $\dcross_H(\bm{t})$, defined in \eqref{eqn:dcross-H}, for any $\bm{t} \in \J(R'_1, ..., R'_{k-2})$, thanks to Statement (2) of Lemma~\ref{lmm:hv:type1:cross-r*}. First, compute $B_\bm{t}$, obtain the rectangle $r' = \gbot(\bm{t})$, and fetch the (already computed) top-sliced rectangle $r^*$ of $r'$; these steps require $O(k)$ time. Then, scan the segments in $\cross_H(r^*)$ in ascending order of their y-coordinates. For each segment $h$ scanned, check whether $h$ belongs to $\dcross_H(\bm{t})$, namely, whether $h$ crosses $B_\bm{t}$ (the reader can verify that $h$ must cross $\gbot(\bm{t})$); this can be done in constant time. Abort the scan as soon as $h \notin \dcross_H(\bm{t})$. This way, we produce $\dcross_H(\bm{t})$ in $O(k + |\dcross_H(\bm{t})|)$ time. Doing so for all $\bm{t} \in \J(R'_1, ..., R'_{k-2})$ takes $O(k \cdot |\J| + \sum_\bm{t} |\dcross_H(t)|) = O(k \cdot \out)$ time, where the derivation used statement (2) of Lemma~\ref{lmm:hv:type1:properties}.

>>>>

\begin{lemma} \label{lmm:hv:type1:properties}
    %Let $r_i$ be the full rectangle of $r_i'$ for each $i \in [k-2]$.
    All the following statements are true:
    \myenums{
        \item Consider any $(k-2)$-tuple $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$. Let $r_i$ ($i$ $\in$  $[k-2]$) be the full rectangle of $\bm{t}[i]$. Then, for any $h \in \dcross_H(\bm{t})$ and any $v \in \dcross_V(\bm{t})$, the $k$-tuple $(r_1, r_2,$ $...,$ $r_{k-2}, h, v)$ must belong to $\J(R_1, ..., R_{k-2}, H, V)$.

        \item Consider any a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v) \in \J_1$. Let $r'_i$ ($i \in [k-2])$ be the trimmed rectangle of $r_i$, and set $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2})$. Then, we must have $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$, $h \in \dcross_H(\bm{t})$, and $v \in \dcross_V(\bm{t})$.

@@

By statements (1) and (2) of Lemma~\ref{lmm:hv:type1:properties}, the set $\J^*$ thus computed indeed satisfies \eqref{eqn:hv:type1:J*}. Furthermore, if we are given $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ for each $\bm{t}$, the above algorithm runs in $O(1 + |\J(R'_1, ..., R'_{k-2})| + k \cdot |\J^*|) = O(1 + k \cdot \out)$ time, where the derivation used \eqref{eqn:hv:type1:J*} and Lemma~\ref{lmm:hv:type1:recur-output}.

@@

\extraspacing {\bf Computing the ``d-cross'' Sets.} We are ready to compute $\dcross_H(\bm{t})$, defined in \eqref{eqn:dcross-H}, for any $\bm{t} \in \J(R'_1, ..., R'_{k-2})$, thanks to Statement (2) of Lemma~\ref{lmm:hv:type1:cross-r*}. First, compute $B_\bm{t}$, obtain the rectangle $r' = \gbot(\bm{t})$, and fetch the (already computed) top-sliced rectangle $r^*$ of $r'$; these steps require $O(k)$ time. Then, scan the segments in $\cross_H(r^*)$ in ascending order of their y-coordinates. For each segment $h$ scanned, check whether $h$ belongs to $\dcross_H(\bm{t})$, namely, whether $h$ crosses $B_\bm{t}$ (the reader can verify that $h$ must cross $\gbot(\bm{t})$); this can be done in constant time. Abort the scan as soon as $h \notin \dcross_H(\bm{t})$. This way, we produce $\dcross_H(\bm{t})$ in $O(k + |\dcross_H(\bm{t})|)$ time. Doing so for all $\bm{t} \in \J(R'_1, ..., R'_{k-2})$ takes $O(k \cdot |\J| + \sum_\bm{t} |\dcross_H(t)|) = O(k \cdot \out)$ time, where the derivation used Lemma~\ref{lmm:hv:type1:recur-output} and statement (3) of Lemma~\ref{lmm:hv:type1:properties}.
